A simulation study of gene flow and local polygenic adaptation motivated by threespine stickleback evolution

### 2018-10-22 Stickleback_Paper.tex

\textbf{Jargon}

effect loci? regions underlying trait value?

names of four allele origin categories

@@

Threespine stickleback fish provide one of the most striking examples of local adaptation. This hemisphere-wide metapopulation includes both marine populations and a large number of smaller freshwater populations
that have apparently repeatedly adapted to freshwater conditions
often using the same genetic basis.
In this paper, we use simulations motivated by stickleback populations
to examine what amounts of gene flow favor stable metapopulation polymorphism
with allele sharing,
and to further dissect the underlying dynamics.
We find that rapid, repeated adaptation 
using alleles maintained at low frequency by migration-selection balance
(the ``transporter hypothesis'')
occurs over a realistic range of intermediate rates of gene flow,
between slow, independent adaptation with low gene flow
and large migration load at high gene flow.
Rapid adaptation occurs when the freshwater haplotype has been maintained,
through historical introgression, in marine environments without tight linkage to 
marine adapted alleles.
We find $F_{ST}$ scans for adaptive alleles are more likely to succeed with higher rates of gene flow.
The results support existing theory of local adaptation,
and provide a more concrete look at a particular, empirically motivated example.

@@

\emph{intro outline:}
Start off with stickleback: repeated, rapid, parallel adaptation with obvious phenotypes.
But, most species don't seem to have such obviously structured polymorphism: 
what's special about stickleback?
The transporter hypothesis is a mechanism; what's required to make it work?
Other species adapt rapidly in similar ways:
e.g., Darwin's finches and island mice;
do these differ through not having such a big, connected reservoir of genetic variation?
or by not having such a large total population size of the ``other'' habitat?
Or, is this situation more common than we know, with less obvious phenotypes?
Also, can we actually tell what's happening from genetic data?

Recently, multiple instances of similar (parallel) underlying genetic basis of rapid local adaptation has brought about 
questions surrounding the origins and maintenance of genetic polymorphism.
A empirical model is the Alaskan populations of freshwater and marine Ninespine Stickleback fish.
In 1964, The Great Alaskan Earthquake caused an uplift of Middleton island and in turn,
introduced a group of freshwater ponds around the perimeter of the island. 
Quickly inhabited by the surrounding marine population of Stickleback,
\citet{lescak2015evolution} observed significant phenotypic changes in less than 50 years that appear to be 
parallel to freshwater stickleback that have been separated for over $13,000$ years.
In freshwater stickleback, the number of lateral plates are reduced
and the opercle shapes shows the same expansion of the dorsal region and reduction of the ventral region.
These results leave us with questions surrounding the nature of rapid adaptation.
Does convergent evolution breed it's own solution (haplotype) for every new selective pressure, 
or can these solutions can be efficiently shared across multiple sub - populations facing similar selective pressures.

The leading hypothesis for stickleback is that rather than acting on new mutations, 
adaptation to freshwater environments is sped up through selection on standing genetic variation (SGV) found in marine populations. 
\jgg{Bill: maybe you could make this section a little more specific}
One clear example of this is the gene \textit{eda} 
which has been shown to regulate the number of lateral plates. 
While this gene arose millions of years ago, it is found in freshwater ponds which have formed much more recently.
Novel evidence from natural populations has provided evidence that most regions of the genome that distinguish marine-freshwater genetic differences share this pattern \citep{nelson2017ancient}.
\citet{schluter2009genetics} 
suggested the ``transporter''-hypothesis.  
This outlined the flow of freshwater alleles into marine populations through offspring of hybridization events.
It suggests freshwater haplotypes are distributed though marine individuals and are continually selected upon in introduced freshwater populations.
The continued selection on freshwater favored alleles and introgression between the two sub-species,
allows the marine to maintain the freshwater haplotype dispersed in low frequency among its' individuals. 
Once a new freshwater environment is introduced and inhabited by marine individuals who carry freshwater adapted alleles, selection reconstructs the freshwater haplotype \citep{schluter2009genetics}.
An alternative to this hypothesis is that individuals from other freshwater environments migrate directly to the new environments, 
and their haplotype is passed down directly. 
This hypothesis has been shown to be unlikely due to finding a high frequency of freshwater alleles in the ocean,
and almost no freshwater individuals.

\plr{Bring up the possibility of more than one freshwater haplotype here.}
\jgg{Re: should I? Doesn't Thom's work and parallel above suggest they have the same alleles?}

If selection on standing genetic variants is key in rapid adaptation, 
many questions are exposed concerning the surrounding population genetics parameters and underlying genomic architecture.
%How rapidly can selection act on standing genetic variants at a given value of migration, $M$?
What scale of historical introgression between populations with selective pressures $X$ and $Y$, allows for rapid and parallel local adaptation
of a population derived from $X$ to an introduced environment with selective pressure $Y$?
What is the origin of pre-existing adaptive variants?
How are the variants structured, historically and across the genome underlying the trait?
%How does population genetics data influenced by historical introgression and selection on standing genetic variants?
%How many alleles underly a certain trait and how many are swept away by drift? 
Furthermore, how can we infer causal loci for regions of the genome that must be driving the rapid adaptation, from real data.
Many biologists today make use of genome wide association studies (GWAS) and 
$F_{st}$ across the genome to estimate regions responsible for certain traits. 
Unfortunately, the data can be heavily influenced by the level of introgression and population structure of the samples. 
This being the case, what are the biases we can expect to see in real data for certain levels of introgression.

There are many different parameters that carry a large impact on the questions above.
\citet{ralph2015convergent} 
explored the dichotomy of selection on new alleles and those brought in by migrants from a similar selective pressure.
Answering the fundamental questions surrounding spatial resolution of convergent evolution. 
%This lead to an understanding of the process by which alleles move from an existing 'patch' to an introduced 'patch' with the 
%same selective pressure. 
\jgg{It seems like this could be a good parallel to what we're doing here, or maybe for discussion?}

In this paper, we explore time to local adaptation as a function of migration rate through an environment (marine) with opposing selective pressure. 
Next, we compare to real data and explore how $F_{st}$ data can be impacted by introgression.
%Explain what we do and what we find that is important

%We use forward moving simulations to model marine and freshwater populations of stickleback.
%We then observe the effect (focusing on migration and recombination, for now) 
%of different parameters on local adaptation of introduced freshwater environments.

@@

We explored these questions
using forwards-time simulations with explicit genomic representation of a quantitative trait
in SLiM \citep{haller2017slim}.
The details (described below) are motivated by previous population genomic studies of threespine stickleback,
but remain simplistic in some aspects due to computational constraints.
\jgg{should we brag about treeSeq here a little?}
Possibly the most important caveat is that simulated population sizes are much smaller
than the census size of the Threespine Stickleback population;
we will consider the likely effects of this in the Discussion.
\plr{TODO}

@@

Fitness in each habitat is determined by a single continuous trait with an inherent tradeoff such that alternative values of the trait have high or low fitness in the two different habitats. This situation roughly models the cumulative effect of the various phenotypes
such as armor morphology, body size, craniofacial variation and opercle shape (among others)
on which divergent selection acts in the two environments.
The optimal trait value in the marine habitat is $+10$,
and in the freshwater habitat is $-10$. Fitness of a fish with trait value $x$ in a habitat with optimal value $x_\text{opt}$ is
Gaussian with standard deviation, i.e.,
\begin{align*}
    f(x; x_0)
    &=
    \exp\left\{
        \frac{1}{2}
            \left(
            \frac{x-x_\text{opt}}{15}
            \right)^2
        \right\} .
\end{align*}

@@

@@

@@

@@

@@

@@

Suppose a new allele enters a lake, either by migration or mutation.
If, when it is rare but present in $n$ copies,
it has fitness advantage $s$
-- i.e., the expected number of copies in the next generation is $(1+s)n$ --
then the probability that it escapes demographic stochasticity to become common in the population
is approximately $2s$ \citep{fisher,prob_fixation}.
If the current population all differed from the optimum trait by $z$,
and the allele has effect size $-u$ in heterozygotes,
then the fitness advantage of the allele would be
$s(u) = \exp(-\beta((z - u)^2) / \exp( - \beta z^2)) \approx 2 \beta z u$,
where in our parameterization, $\beta = 1 / 450$.
This tells us two things:
(1) the rate of adaptation decreases as the population approaches the optimum,
and (2) larger mutations (in the right direction) are more likely to fix.

@@

These calculations depend on there being no bottleneck in colonization of the lake;
if there is a bottleneck, then an additional factor must be added.

At what point do we expect new mutation to be more important than migration for adaptation?
By the calculations above, if $M \ge 10$, we expect initial diversity in a lake to be sufficient 
for adaptation, corresponding to our third-highest migration rate.
If this does not happen, then we expect adaptation to take a multiple of $1/m$ generations;
with our values, $1/m$ ranges from 20,000 to 20 generations.
Above we estimated that adaptive alleles due to new mutation fix locally about every 2,000 generations,
suggesting that at our second-lowest migration rate (where $1/m = 2,000$),
the two contributions of migration and new mutation are roughly equal.
This is in fact what we see: in Figure \ref{fig:MPFAI},
we see that at the second migration rate, alleles start to be shared between lakes,
while by the third migration rate, they are almost entirely shared.

@@

We have also shown introgression is beneficial for inferring causative loci from divergence ($F_{st}$) along the genome. 
This is generally because noise of selectively neutral alleles divergence can appear causative when genetic drift causes more 
differences between populations that have little gene flow between them.
It's important to know that in all scenarios, hitchhiking of selectively neutral alleles could also be 
mistaken for being causative as they often display the same amount of divergence.
%wouldn't it be cool if we could use this fact and simulate introgression, starting with real data that is noisy to extrapolate the areas we care about?
%this could be nonsense

>>>>

@@

Threespine stickleback fish provide a striking example of local adaptation in the context of recurrent gene flow. This Northern hemisphere-wide metapopulation includes both marine populations and a large number of smaller freshwater populations that have repeatedly adapted to freshwater conditions, often by using standing genetic variation. Here we use genealogical simulations to determine the levels of gene flow can best match the observed patterns of allele sharing among habitats in stickleback, and to provide a framework for better understanding of the dynamics of gene flow and local adaptation for the maintenance and reuse of standing genetic variation. We find that rapid, repeated adaptation using alleles maintained at low frequency by migration-selection balance occurs over a realistic range of intermediate rates of gene flow.  Slow and independent adaptation occurs with low gene flow, whereas large migration load occurs at high gene flow, mediated mainly by the total downstream influx of alleles \emph{(maybe??)}. We do not see evidence for strong effects encouraging genomic clustering of causal alleles or towards particular dominance coefficients. $F_{ST}$ scans for adaptive alleles are more likely to succeed with higher rates of gene flow, The results support existing theory of local adaptation, and provide a more concrete look at a particular, empirically motivated example.

\textbf{**We need to be more crystal clear in the abstract about the findings from the paper**}

@@

The canonical model for the genetics of adaptation, first formulated by Fisher in the early part of the 20th century, involves the sequential fixation of new mutations. While it has proven valid in numerous studies in the field and the lab, this model is now rightfully understood as incomplete for many species in nature that have more complicated population structures. A growing number of studies have identified instances of convergent or parallel adaptive evolution that utilize standing genetic variation. What evolutionary processes promote the maintenance of re-use of such genetic polymorphisms? How do these processes interact with diverse geographic contexts, as well as variation in genetic processes such as recombination, to change the likelihood of so-called standing genetic variation (SGV).

Clues come from population genomic studies in the wild that have recently been powered by advances in sequencing technologies. One such organism is the threespine stickleback. This small fish has long been used for studies of behavior, ecology and evolution in the wild, and has more recently become a model for understanding the genetic basis of adaptive evolution. The ancestral marine form has given rise to millions of independently derived populations in recently de-glaciated regions of the Northern Hemisphere, which have each evolved a similar suite - or 'freshwater syndrome' - of phenotypes despite local differences. This adaptive phenotypic evolution to freshwater can occur in mere millenia, in many cases since the end of the last ice age about 13,00 years ago. Studies of the fossil record also clearly show that invasion of oceanic stickleback and local adaptation in freshwater has occurred repeatedly over millions of years, often involving very similar phenotypic shifts as seen in contemporary populations.

A finding from recent stickleback population genomic studies is that the same genomic regions, and in some cases the same haplotypes, are implicated in patterns of repeated evolution. These studies show that divergent stickleback populations are clearly still connected via bi-directional gene flow. This reuse of standing genetic variation motivated empirical studies to ask whether this phenotypic and genomic evolution could occur in decades. The answer is a clear yes. For example, in 1964 the Great Alaskan Earthquake caused an uplift of Middleton island and in turn, introduced a group of freshwater ponds around the perimeter of the island. Quickly inhabited by the surrounding marine population of stickleback, \citet{lescak2015evolution} observed significant phenotypic changes in less than 50 years that appear to be parallel to freshwater stickleback that have been separated for over thousands of years. In freshwater stickleback, the number of lateral plates are reduced and the opercle shapes shows the same expansion of the dorsal region and reduction of the ventral region.

 But how can evolution occur so quickly? The leading hypothesis for stickleback is that rather than acting on new mutations, adaptation to freshwater environments is accelerated by selection on SGV found in marine populations. The first clear example of the global reuse of SGV was the gene \textit{eda} which has been shown to be an important regulator for the number of lateral plates. While the low lateral plate version of this gene arose millions of years ago, it is found in freshwater ponds which have formed much more recently. More recently, population genomic studies employing genome-wide haplotype analyses has provided evidence that most regions of the genome that distinguish marine-freshwater genetic differences share this pattern \citep{nelson2017ancient}. Genomic regions that exhibit local adaptation, as evidenced by increased relative population genomic divergence, also show much older haplotypes that are enriched in the alternative habitats.

These empirical data generally support the ``transporter''-hypothesis proposed by Conte and Schluter in 2009 \citet{schluter2009genetics}, which is a conceptual model for the flow of freshwater alleles from multiple smaller freshwater populations into much larger and less structured marine populations through hybridization events. Alleles in this asymetrically structured metapopulation can then be recycled for subsequent freshwater adaptation. Several questions remain, however, about the manner and degree to which these alleles are scattered among the marine fish and must be re-assembled. Is it more akin to the atomization and rebuilding that occurred in the Star Trek series that motivated this hypothesis? Alternatively does it occur in more of a patchwork by individuals, or their early generation hybrids, in geographically adjacent freshwater habitats moving quickly through the marine environment to seed new freshwater populations. More generally, how do different levels of gene flow and local adaptation interact with the asymmetric nature of stickleback population structure affect the dynamics of the origin and rate of adaptive alleles, as well as their eventual organization into marine and freshwater typical genomes?

Here we develop a forward simulation approach in SLiM to model the stickleback population structure in marine and freshwater habitats to document the effect of variation in gene flow and recombination on the genetic and genomic architecture of local adaptation. We address how rapidly can selection act on standing genetic variants at a given value of migration, $M$, and what the precise origin is of those variants. We ask what scale of historical introgression between populations with selective pressures $X$ and $Y$, allows for rapid and parallel local adaptation of a population derived from $X$ to an introduced environment with selective pressure $Y$? How are the variants structured, historically and across the genome underlying the trait? Furthermore, how can we infer causal loci for regions of the genome that must be driving the rapid adaptation, from real data. Many biologists today make use of genome wide association studies (GWAS) and $F_{st}$ across the genome to estimate regions responsible for certain traits. Unfortunately, the data can be heavily influenced by the level of introgression and population structure of the samples. This being the case, what are the biases we can expect to see in real data for certain levels of introgression.

We find that .... \textbf{1. rewrite the previous paragraph to be more concise and tight, and 2. briefly restate our major findings which should line up well with those presented in the abstract. The following I grabbed from the beginning of the Results section}
*****
We varied the migration rate, $m$, from $5 \times 10^{-5}$ to $5 \times 10^{-2}$ per individual, i.e., between 0.01 and 10 migrants per year to and from each of the ten lakes. This had a strong effect on many aspects of adaptation, including how fast adaptation occurred in each lake, how much alleles were shared between lakes,
and the population genetic signals left behind. At the lowest migration rate, lakes adapted nearly independently, while at the highest migration rate, the habitats are beginning to act like a single metapopulation with substantial migration load. We will now dissect what happens between these extremes. Interestingly, the ability for separate populations to locally adapt to their own selective pressure was relatively unaffected until the highest rate of migration between the marine and freshwater environments. All rates of historical introgression aside from the lowest, helped both the initial and introduced freshwater populations share pre-existing freshwater adapted alleles. The sharing of alleles resulted in rapid adaptation ($\approx 100$ generations) of the introduced population (split from the marine population) to adapt to the freshwater environment. We also found that larger amounts of migration allow for more statistical power and less false positives in the resulting population genetics data ($F_{st}$ per SNP across the genome).
****

@@

We explored these questions using forwards-time simulations with explicit genomic representation of a quantitative trait in SLiM \citep{haller2017slim}. 
The details (described below) are motivated by previous population genomic studies of threespine stickleback, but remain simplistic in some aspects due to computational constraints.
Possibly the most important caveat is that simulated population sizes are much smaller than the census size of the threespine stickleback population;
we will consider the likely effects of this in the Discussion. \plr{TODO}

@@

Fitness in each habitat is determined by a single continuous trait with an inherent tradeoff such that alternative values of the trait have high or low fitness in tht two different habitats. 
This situation roughly models the cumulative effect of the various phenotypes such as armor morphology, 
body size, craniofacial variation and opercle shape (among others) on which divergent selection acts in the two environments. 
The optimal trait value in the marine habitat is $+10$, and in the freshwater habitat is $-10$. 
Fitness of a fish with trait value $x$ in a habitat with optimal value $x_\text{opt}$ is Gaussian with standard deviation, i.e.,

\begin{align*}
    f(x; x_0)
    &=
    \exp\left\{
        \frac{1}{2}
            \left(
            \frac{x-x_\text{opt}}{15}
            \right)^2
        \right\} .
\end{align*}

@@

\paragraph{Initial genomic architecture} Each individual carries two copies of a linear chromosome of $10^8$ loci(which could be thought of roughly as a kilobase each). 
New mutations occur with probability $10^{-7}$ per locus per generation. 
Ten ``effect regions'' of $100Kb$ loci each are spread evenly along the chromosome (separated by 4950 loci) in which mutations affect the trait; 
mutations in other parts of the genome are neutral. 
Each mutation in these regions is either additive, completely recessive, or completely dominant (with equal probability), 
and with an effect sizes chosen randomly from an Exponential distribution with mean $1/2$, either positive or negative with equal probability. 
Individual trait value are determined additively from the diploid genotypes. 
Concretely, an individual that is heterozygous and homozygous for mutations at loci $H$ and $D$ respectively has trait value 
$x = \sum_{\ell \in H} h_\ell s_\ell + \sum_{\ell \in D} s_\ell$, 
where $s_\ell$ is the effect size of the mutation at locus $\ell$. Subsequent mutations at the same locus replace the previous allele.

\paragraph{Equilibrium in initial marine and freshwater populations} 
Each generation, the two parents of each new offspring are chosen proportional to their fitness 
(all individuals are hermaphroditic),
and the contributing genomes are produced by Poisson recombination with an average of one crossover per chromosome per generation 
($10^{-7}$ per locus per generation). 
The model is Wright-Fisher, so that each generation, in each habitat, 
2000 new individuals are produced, and so to keep population sizes roughly constant within each lake, 
at the start of each generation we rescale fitness values in the freshwater habitat so that the sum of the fitness values within each lake are equal.

Migration occurs both locally along the coastline in the marine habitat and between the marine habitat and the lakes, and can be thought of as occurring at the juvenile stage. 
The between-habitat migration rate is denoted $m$, and will be called simply the ``migration rate''. 
Each new individual in the marine habitat has freshwater parents with probability $m$; 
to obtain the pair, a first parent is chosen proportional to fitness, and a mate is chosen from the same lake as the first, also proportional to fitness. 
The resulting offspring is given a spatial location in the marine habitat at the location of the parent's lake. 
Parents for a new marine individual who is not a migrant are chosen similarly (with probability $1-m$): 
first, a single parent is chosen proportionally to fitness in the marine habitat,
and then a mate is chosen, also proportionally to fitness but re-weighted by a Gaussian function of the distance separating the two, with stanadard deviation $1/2$.

Concretely, if the first parent is marine individual $i$, then marine individual $j$ is chosen as the mate with probability proportional to $f(x_i) \exp(-2d_{ij}^2)$,
where $d_{ij}$ is the distance between the two locations. 
Finally, each new marine offspring is given a position displaced from the first parent's position by a random Gaussian distance with mean 0 and standard deviation 0.02, 
and reflected to stay within the population. 
New offspring in the freshwater habitat are chosen in the same way, except the probability that the parents are marine individuals is $m$; 
any new freshwater offpsring produced by marine individuals are assigned to the lake nearest to the position of the first marine parent.

\paragraph{Population genomic analyses of new freshwater populations} 
To study adaptation in newly appearing freshwater habitats, we introduce a new set of lakes midway through the simulation. 
The initial set of individuals have parents chosen as above from the marine habitat, 
and act like an independent copy of the original set of lakes -- in particular, 
the two sets of lakes each have 2,000 individuals at all times. 
Since this doubles the number of lake-to-marine immigrants, after this happens the probability that a new marine individual has freshwater parents is $2m$ instead of $m$.

To assess whether new lakes adapt using existing genetic diversity, we define a \emph{pre-existing freshwater adapted allele}
to be an effect mutation that has frequency higher than $0.5$ in at least one of the original lakes, while remaining lower than $0.5$ in the marine. 
This categorization is made for each generation using the allele frequencies from that generation, and so changes with time. Alleles common in the newly introduced lakes do not count
if they are not also common in the original lakes. 
They are defined this way because the transportation hypothesis does not specify where or when an advantageous mutation arises, 
but simply suggests that any sufficiently common freshwater adapted allele could participate in adaptaiton in new habitat \citep{schluter2009genetics}.

\emph{Time to adaptation} of the introduced population, denoted $T_\text{adapt}$, is defined to be the generation at which the difference between the average trait value in the original and the introduced freshwater populations is less than 0.5. 
We describe overall genetic differentiation between the habitats using $F_{ST}$,
calculated on a per-locus basis. Concretely, if $p_f$ and $p_m$ are the frequencies of a given mutant allele in the freshwater and marine habitats, respectively,
and $\bar p = (p_f + p_m)/2$, then we compute $F_{ST}$ for that mutation as $1 - p_f p_m / (\bar p (1-\bar p))$.

@@

\begin{comment}
\paragraph*{Rate of adaptation}
Increasing migration rate strongly decreased the time until freshwater habitats could adapt, both in the initial and introduced sets of lakes. As shown in Figure \ref{fig:TimeToAdaptation}, at the lowest migration rate it took over 20 thousand generations for the mean trait value across introduced lakes to get to within 0.5 of the original lakes value. Although many lakes had adapted before this time, the different rates of introduction of effect alleles is clearly seen in the traces of trait values against time (e.g., Figure \ref{fig:phenotype_ts2}). However, higher migration rates allowed the freshwater habitat to adapt nearly as quickly as the marine habitat.
\end{comment}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Sharing of freshwater adapted alleles}

%FIGURES THAT SHOW THIS:
%-MPAA / IND
%-Total/Avg shared
\begin{comment}
The tenfold difference in speed of adaptation occurs because at low migration rates, adaptation occurs independently in each lake,and the marine habitat has ten times the influx of new alleles than any one lake. In other words, greater mixing at higher migration rates allows lakes to share alleles instead of developing their own genetic basis of adaptation. As a first indication of this, Figure \ref{fig:Fst} shows that $F_{ST}$ between the ``original'' and ``introduced'' sets of lakes at effect mutations decreased with migration rate.

To further investigate sharing of locally adaptive alleles and the transporter hypothesis, we investigate the ``pre-existing freshwater adapted alleles'',
defined for a particular generation to be effect mutations above 50\% in at least one original lake and below 50\% in the marine habitat in that generation.
Figure \ref{fig:MPFAI}A shows the distribution of the number of these alleles, across generations, as well as the average number of lakes each is found in. As migration rates increase, the number of these alleles decreases steadily, and each is concurrently found in a greater number of lakes.

As the number of common, locally adaptive alleles decreases, the genetic basis of adaptation is more commonly shared. Figure \ref{fig:MPFAI}B shows the distribution of the mean percentage of currently-defined freshwater adapted alleles that each genome in each of the populations carries, averaged across time and individuals. If all individuals across lakes carried the same set of alleles determining their trait value, this would be 100\%. This value is nearly reached at the highest migration rate; but it is lower due to migration load. At the lowest migration rate, each genome in the original lakes have almost exactly $1/10^{th}$ of the total freshwater adapted alleles -- since there are 10 lakes, this implies that each lake has adapted with a unique set of alleles. Since these are \emph{pre-existing} alleles, the value is zero for introduced lakes.
\end{comment}

@@

\begin{comment}
At first, increased migration allows sharing of adaptive alleles between lakes, but at the highest migration rate, the constant influx of alleles between the habitats creates substantial migration load. This rate, $m=.05$, only replaces 5\% of each population each generation with migrants from the other habitat, but this is sufficient to shift the mean trait values to nearly half their optimal values, as seen in Figure \ref{fig:MeanPhenotype}. Significant gene flow constricts local adaptation as a consequence of a large number of offspring through hybridization events between subpopulations.

\paragraph{Standing genetic variation} Despite a dramatic difference in the amount of allelic sharing between lakes, standing genetic variance (Figure \ref{fig:SGV}) was around 0.05 in the freshwater habitat across all but the highest migration rates. Concurrently, genetic variation in the marine population steady increased with migration
to a similar value. On the one hand, it is not surprising that lakes, as a group, carry more genetic variation than the marine habitat, since population subdivision allows different alleles to become common in each. However, it is striking that at $m=.005$, the marine habitat carries as much genetic variation, despite a lack of any substantial migration load.

\end{comment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{comment}
\subsection*{Realized genomic architecture}
Now we take a closer look at the genomic architecture of local adaptation between the two habitats. Do the alleles underlying trait differences cluster along the genome?
Do measures of local differentiation identify the causal loci? Figure \ref{fig:Fst3} shows plots along the genome of per-locus $F_{ST}$ values between the marine and original freshwater habitats at the two intermediate migration rates. (Note that we are pooling freshwater habitats; a single lake would provide substantially less power.)

\plr{need to know where the FAA are in these figures}

Higher migration rates showed more distinct $F_{ST}$ peaks over polymorphic loci underlying trait differences between the habitats. As migration rate decreased, the ``background'' levels of $F_{ST}$ increased, swamping out this signal until the regions under selection were indistinguishable. This is likely due to two reasons: first, stronger genetic drift with less migration leading to higher background $F_{ST}$, and second, greater sharing of adaptive alleles providing a shared signal across populations.

This suggests that genome scans for local adaptation based purely on measures of differentiation will only be successful given enough migration between habitats. To quantify this, Figure \ref{fig:Power_FP} shows the power and false positive rates that would be obtained by an $F_{ST}$ cutoff that declared everything above a certain value to be a causal locus.

\plr{Labels are wrong on that figure: false pos rate should go down with cutoff.
     Is it true positive rate?}

In regions of the genome underlying individual trait value, we observed Given that migration increases the gene flow between subpopulations, how valid are $F_{st}$ peaks at different $M$. Knowing exactly which mutations effect phenotype in our simulations, we can look at the statistical power and false positives given $F_{st}$ per SNP across the genome. In Figure \ref{fig:Power_FP} , looking at an $F_{st}$ threshold greater than 1, we see the two lowest migration rates $10^{-5}$ and $10^{-4}$ having very little statical power. This along with low false positive rate across all $F_{st}$ threshold values is fairly predictable when you consider the high $F_{st}$ values across the genome. 
\end{comment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Suppose a new allele enters a lake, either by migration or mutation. If, when it is rare but present in $n$ copies, it has fitness advantage $s$ -- i.e., the expected number of copies in the next generation is $(1+s)n$ --then the probability that it escapes demographic stochasticity to become common in the population is approximately $2s$ \citep{fisher,prob_fixation}. If the current population all differed from the optimum trait by $z$, and the allele has effect size $-u$ in heterozygotes, then the fitness advantage of the allele would be $s(u) = \exp(-\beta((z - u)^2) / \exp( - \beta z^2)) \approx 2 \beta z u$, where in our parameterization, $\beta = 1 / 450$. This tells us two things: (1) the rate of adaptation decreases as the population approaches the optimum, and (2) larger mutations (in the right direction) are more likely to fix.

@@

These calculations depend on there being no bottleneck in colonization of the lake; if there is a bottleneck, then an additional factor must be added. At what point do we expect new mutation to be more important than migration for adaptation? By the calculations above, if $M \ge 10$, we expect initial diversity in a lake to be sufficient  for adaptation, corresponding to our third-highest migration rate. If this does not happen, then we expect adaptation to take a multiple of $1/m$ generations;
with our values, $1/m$ ranges from 20,000 to 20 generations. Above we estimated that adaptive alleles due to new mutation fix locally about every 2,000 generations, suggesting that at our second-lowest migration rate (where $1/m = 2,000$), the two contributions of migration and new mutation are roughly equal.
This is in fact what we see: in Figure \ref{fig:MPFAI}, we see that at the second migration rate, alleles start to be shared between lakes, while by the third migration rate, they are almost entirely shared.

@@

We also have also explored the genomic architecture as a consequence of the nature of selection in our scenario. The alleles underlying individual trait value were of large effect and a low number. With a total of $10^{5}$ loci, to be realistic, each loci should represent 1000 $Kb$ in real data.

We have also shown introgression is beneficial for inferring causative loci from divergence ($F_{st}$) along the genome. 
This is generally because noise of selectively neutral alleles divergence can appear causative when genetic drift causes more 
differences between populations that have little gene flow between them.
It's important to know that in all scenarios, hitchhiking of selectively neutral alleles could also be 
mistaken for being causative as they often display the same amount of divergence.
>>>>>>> master
%wouldn't it be cool if we could use this fact and simulate introgression, starting with real data that is noisy to extrapolate the areas we care about?
%this could be nonsense
